### 2013-09-26 Tex/chapters/results.tex
Bruchstriche in Exponenten entfernt

            \bottomrule
        \end{tabular}
        \caption[Critical Exponents for Different $\sigma$]{
            Critical exponents for different values of \(\sigma\). A finite size
            scaling analysis was performed to determine the critical
            exponents \(\beta, \gamma, \nu\) and the critical temperature
            \(T_c\). The errors for \(\beta\) and \(\gamma\) are estimated
            by \texttt{autoscale.py} \cite{autoscale2009}. The errors of
            \(\nu\) and \(T_c\) are the standard deviation of three obtained
            values through different collapses (see text).
        }
        \label{tab:critExp}
    \end{table}\\
    According to Tab.\ \ref{tab:critExp}, most values
    are matching the expectations.
    \(T_c\) for \(\sigma = 0\) is in good
    agreement with the known value. Especially \(\nu\) and \(\gamma\)
    are always in very good agreement with their exact values. Besides the
    good agreement of the values of \(\nu\) and \(\gamma\) obtained by data collapse,
    the ratio \(\frac{\gamma}{\nu}\) is also determined by fitting the maxima of
    the susceptibility \(\chi_{\mathrm{max}}\) to the power law function \(aL^\frac{\gamma}{\nu}\).
    Because this should only be a rough check, if the exponents obtained
    by the collapse are valid, it should give a
    reasonable estimate to take their maximum, without any kind of interpolation.
    The results are displayed in Fig.\ \ref{fig:susCrossCheck}. The ratios
    determined by this method confirm the values obtained by collapse.
    \begin{figure}[htbp]
        \centering
        \subfigure[for a RNG][]
        {
            \label{sfig:susCrossCheck:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNGgammaBySus}
        }
        \subfigure[for a GG][]
        {
            \label{sfig:susCrossCheck:GG}
            \includegraphics[width=0.45\textwidth]{plots/GGgammaBySus}
        }
        \caption[Alternative Way Determining $\gamma / \nu$]
        {
            Cross checking the ratio of the critical exponents $\gamma$ and $\nu$ for
                \subref{sfig:susCrossCheck:RNG} the RNG at $\sigma \in \{0.0, 1.0\}$ and
                \subref{sfig:susCrossCheck:GG} the GG at $\sigma \in \{0.0, 0.3\}$.
            The plotted values are the maxima of all measured \(\chi\).
            Dotted lines are fits to the power law function \(aL^\frac{\gamma}{\nu}\).
        }
        \label{fig:susCrossCheck}
    \end{figure}\\
    Despite the very good results for \(\nu\) and \(\gamma\), most of the
    \(\beta\) seem to be a bit too big -- especially for the RNG -- but
    they are close enough to the expectations to be consistent. At least
    the expectations are always within two times the uncertainty.
    Maybe their deviations can be explained by the fact that small
    systems (\(L=32,64\)) were used for the analysis and no corrections
    to scaling terms were considered.
    Anyway, two critical exponents are sufficient to determine the
    universality class \cite[p. 145]{Katzgraber2011}. Therefore,
    the Ising model on a proximity graph is for every \(\sigma\) in the
    same universality class as the square lattice Ising ferromagnet.

>>>>

            \bottomrule
        \end{tabular}
        \caption[Critical Exponents for Different $\sigma$]{
            Critical exponents for different values of \(\sigma\). A finite size
            scaling analysis was performed to determine the critical
            exponents \(\beta, \gamma, \nu\) and the critical temperature
            \(T_c\). The errors for \(\beta\) and \(\gamma\) are estimated
            by \texttt{autoscale.py} \cite{autoscale2009}. The errors of
            \(\nu\) and \(T_c\) are the standard deviation of three obtained
            values through different collapses (see text).
        }
        \label{tab:critExp}
    \end{table}\\
    According to Tab.\ \ref{tab:critExp}, most values
    are matching the expectations.
    \(T_c\) for \(\sigma = 0\) is in good
    agreement with the known value. Especially \(\nu\) and \(\gamma\)
    are always in very good agreement with their exact values. Besides the
    good agreement of the values of \(\nu\) and \(\gamma\) obtained by data collapse,
    the ratio \(\frac{\gamma}{\nu}\) is also determined by fitting the maxima of
    the susceptibility \(\chi_{\mathrm{max}}\) to the power law function \(aL^{\gamma/\nu}\).
    Because this should only be a rough check, if the exponents obtained
    by the collapse are valid, it should give a
    reasonable estimate to take their maximum, without any kind of interpolation.
    The results are displayed in Fig.\ \ref{fig:susCrossCheck}. The ratios
    determined by this method confirm the values obtained by collapse.
    \begin{figure}[htbp]
        \centering
        \subfigure[for a RNG][]
        {
            \label{sfig:susCrossCheck:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNGgammaBySus}
        }
        \subfigure[for a GG][]
        {
            \label{sfig:susCrossCheck:GG}
            \includegraphics[width=0.45\textwidth]{plots/GGgammaBySus}
        }
        \caption[Alternative Way Determining $\gamma / \nu$]
        {
            Cross checking the ratio of the critical exponents $\gamma$ and $\nu$ for
                \subref{sfig:susCrossCheck:RNG} the RNG at $\sigma \in \{0.0, 1.0\}$ and
                \subref{sfig:susCrossCheck:GG} the GG at $\sigma \in \{0.0, 0.3\}$.
            The plotted values are the maxima of all measured \(\chi\).
            Dotted lines are fits to the power law function \(aL^{\gamma/\nu}\).
        }
        \label{fig:susCrossCheck}
    \end{figure}\\
    Despite the very good results for \(\nu\) and \(\gamma\), most of the
    \(\beta\) seem to be a bit too big -- especially for the RNG -- but
    they are close enough to the expectations to be consistent. At least
    the expectations are always within two times the uncertainty.
    Maybe their deviations can be explained by the fact that small
    systems (\(L=32,64\)) were used for the analysis and no corrections
    to scaling terms were considered.
    Anyway, two critical exponents are sufficient to determine the
    universality class \cite[p. 145]{Katzgraber2011}. Therefore,
    the Ising model on a proximity graph is for every \(\sigma\) in the
    same universality class as the square lattice Ising ferromagnet.
